Bootstrapping Multi-atlas Hippocampal Segmentation with MAGeT

### 2013-02-26 paper.Rnw
Added SFEP dataset method details

\subsubsection{Schizophrenic First Episode Patients}
\todo{Nomenclature: SFEP Dataset}
\todo{describe image characteristics}
\todo{describe expert segmentations}
SFEP dataset demographics are shown in table \ref{tab:SZFEP_Demographics}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First Episode SZ Demographics Table                                         %
%                                                                             %
<<FEP-SZ-demographics, echo=F, results="asis",cache=FALSE>>=
fep_sz_demographics = read.csv("data/SZ_demographics.csv", na.strings=c("","."))
fep_sz_demographics = subset(fep_sz_demographics, Anon <= 81)
tab <- summary(DX ~ Age + Gender + Handedness + Education + SES + FSIQ,
               data=fep_sz_demographics, method = "reverse", test = FALSE)
latex(tab, file="", size="scriptsize", ctable=FALSE,
      caption="Schizophrenia First Episode Patient Demographics",
      title="tab:SZFEP_Demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\todo{Include a description of validation process.. Note that we could use rms
{\tt validate} or t-test: contrast with QDA or LDA (Coupe 2011) used in LOOCV,
with adni/our segmentations}

@@

\begin{figure}
<<ADNI1_cross_validation_means, cache=TRUE, fig=TRUE>>=
t_data       = read.csv(file='data/a2a_tracc_results_2012_08_30.csv')
a_data       = read.csv(file='data/a2a_ants_results_2012_08_30.csv')

@@

\begin{figure}
<<ADN1-cross-validation-MA-difference, cache=TRUE, fig=TRUE>>=
ggplot(all_data, aes(x=num_templates, y=k_minus_ma, colour=as.factor(num_atlases))) + 
  facet_grid(method ~ reg_method) + 
  geom_smooth() + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean Kappa between voting method and multiatlas" )
@
  \caption{Difference in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}

>>>>

\subsubsection{Schizophrenic First Episode Patients}
All patients were recruited and treated through the Prevention and Early
Intervention Program for Psychoses (PEPP-Montreal), a specialized early
intervention service at the Douglas Mental Health University Institute in
Montreal, Canada. People aged 15–30 years from the local catchment area
suffering from either affective or non-affective psychosis who had not taken
antipsychotic medication for more than one month with an IQ above 70 were
consecutively admitted as either in- or out-patients. Of those treated at PEPP,
only patients aged 18 to 30 years with no previous history of neurological
disease or head trauma causing loss of consciousness were eligible for the
neuroimaging study; only those suffering from schizophrenia spectrum disorders
were considered for this analysis.  For complete program details see Malla et
al. \citep{Malla2003}.

Scanning was carried out at the Montreal Neurological Institute on a 1.5-T
Siemens whole body MRI system.  Structural T1 volumes were acquired for each
participant using a three-dimensional (3D) gradient echo pulse sequence with
sagittal volume excitation (repetition time=22ms, echo time=9.2ms, flip
angle=$30{\circ}$, 180 1mm contiguous sagittal slices). The rectangular field-of-view
for the images was 256mm (SI)×204mm (AP).  Subject demographics are shown in
table \ref{tab:SZFEP_Demographics}.

The hippocampus were traced following a validated protocol developed by Dr Jens
Pruessner (Pruessner et al., 2000). A recent update to this protocol by Dr J
Pruessner in 2006 allows to accurately and consistently subdivide the
hippocampus into three different subregions: head, body, and tail.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First Episode SZ Demographics Table                                         %
%                                                                             %
<<FEP-SZ-demographics, echo=F, results="asis",cache=FALSE>>=
fep_sz_demographics = read.csv("data/SZ_demographics.csv", na.strings=c("","."))
fep_sz_demographics = subset(fep_sz_demographics, Anon <= 81)
tab <- summary(DX ~ Age + Gender + Handedness + Education + SES + FSIQ,
               data=fep_sz_demographics, method = "reverse", test = FALSE)
latex(tab, file="", size="scriptsize", ctable=FALSE,
      caption="Schizophrenia First Episode Patient Demographics",
      title="tab:SZFEP_Demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

\begin{figure}
<<ADNI1_cross_validation_means, cache=TRUE>>=
t_data       = read.csv(file='data/a2a_tracc_results_2012_08_30.csv')
a_data       = read.csv(file='data/a2a_ants_results_2012_08_30.csv')

@@

\begin{figure}
<<ADN1-cross-validation-MA-difference, cache=TRUE>>=
ggplot(all_data, aes(x=num_templates, y=k_minus_ma, colour=as.factor(num_atlases))) + 
  facet_grid(method ~ reg_method) + 
  geom_smooth() + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean Kappa between voting method and multiatlas" )
@
  \caption{Difference in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}
